BivData Setup

### 2020-02-03 src/BivData_Setup.Rmd
lots of cleaning up and de-bugging

calq the nromalized.siscoten, double check the negative values; 13sep18_28jun18_MOLF_m1_sp1_18.1_rev_14, 27aug15_12jun15_WSB_m2_sp1_18_rev_18, 21nov17_16nov17_MSM_f3_sp1_3_rev_1

foci.pass = 2  5aug17_14jul17_MSM_f1_sp1_13_rev_3

hand foci =0 but there is a foci position

too high hand foci count

@@

#BIVDATA MASTER SHEET
new.Curate.FULL <- read.csv("~./MLH1repo/data/BivData/curation/FULL_Curated_BivData.csv")
#83976
#83009
#80898
#80919
#61084
#60241
#60830

#Clean away all the empty rows
new.Curate.FULL <- new.Curate.FULL[!(is.na(new.Curate.FULL$fileName) | new.Curate.FULL$fileName==""), ]

@@

```{r split.up.DF, echo=FALSE}

#new.Curate.FULL to Curated_BivData

#SC PASS
new.Curate.FULL <- new.Curate.FULL[new.Curate.FULL$SC.pass == '1',]#10480 #9819, #9769

@@

Foci_TRUE_Curate_BivData <-   Curated_BivData[(!is.na(Curated_BivData$hand.foci.count)),]
```

@@

just.SC.length <- Curated_BivData[is.na(Curated_BivData$hand.foci.count),]#650 lines

#table(just.SC.length$category)
#decide what to do with these lines
#how will they be represented in Mat Methods?
```

@@

@@

#neg Nrm F1
#negative.IFD2 <- Curated_BivData[which(Curated_BivData$PER_Foci_1 < 0),]
#0 really?
```

@@

I'm considering removing the same mice from the MLH1 counts, from the BivData, but this might -- limit the comparisons -- might be too stict. IF foci are bright and clear, SC/bivalents intact -- include.

IF it seems like primary reason for excluding is low cell number include bivalents

@@

- the reasons for poor quality of the exclude mice in above list, might be from 2-3 bad bivalents -- which are removed from the biv data during the curation process.

```{r set.type, echo=FALSE}
##change factor cols to numbers (factor -> chr -> number)
Curated_BivData$centromere_ABS_Position <- as.character(Curated_BivData$centromere_ABS_Position)
Curated_BivData$centromere_PER_Position <- as.character(Curated_BivData$centromere_PER_Position)
Curated_BivData$chromosomeLength <- as.character(Curated_BivData$chromosomeLength)

- HetC_MM  : subset only mice

IFD functions

  - IFD: currently I think just does 2CO bivalents

  - IFD.2: for mulitple IFDs (3CO ect.)

## Strain specific data sets

@@

## Male specific data set

@@

#these measure ect should be in the male - mouse 
#isolate all musc and male
Curated_BivData_male <- Curated_BivData[ (Curated_BivData$sex == "male") & (Curated_BivData$species == "Musculus"),]

#make table
SC.Length.male_table <- ddply(Curated_BivData_male, c("strain"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

@@

# Manual Whole Cell

@@

#PER Foci

```{r clean.whole.cell, echo = FALSE}

@@

# Cell Level table

@@

                       mean.IFD_2C0 = mean(   IFD1_ABS[which(hand.foci.count == 2)], na.rm = TRUE),
                      var.IFD_2CO = var( IFD1_ABS[which(hand.foci.count == 2)], na.rm=TRUE),
                       #sd.IFD_2CO   = round(sd(IFD1, na.rm=TRUE), 3),
                       #se.IFD_2CO   = round(sd.IFD / sqrt(nbivs), 3)

#cent_dis
                      mean_cent_dist = mean(dis.cent, na.rm=TRUE)
#telomere dist

#can't think of a why to calq this by just 2CO

)
                       #add the centromere and ifd here?
                       #mean.dist_cent = mean(dis.cent, na.rm=TRUE),
#                       var.dist_cent = var(dis.cent, na.rm=TRUE),
#                       sd.dist_cent   = round(sd(dis.cent, na.rm=TRUE), 3),
#                       se.dist_cent   = round(sd.dist_cent / sqrt(nbivs), 3),

@@

as.data.frame( head(cell.level.BivData_table) )

@@

# Long Biv Data Set

@@

#1. how many biv's are from cells with >15 bivalents
over_15_biv_cell_DF <- cell.level.BivData_table[cell.level.BivData_table$Nbiv >15, ]
BivData_from_15biv_cells <- Curated_BivData[ Curated_BivData$fileName %in% over_15_biv_cell_DF$fileName, ]

@@

#check for dup
#length(duplicated(BivData_from_15biv_cells$Obj.ID))#2605
#anyDuplicated(BivData_from_15biv_cells$Obj.ID)#1997
dups.dummy <- BivData_from_15biv_cells[duplicated(BivData_from_15biv_cells$Obj.ID),]

@@

#make sure obj.id and fileName are charcter for str stuff
BivData_from_15biv_cells$fileName <- as.character(BivData_from_15biv_cells$fileName)
BivData_from_15biv_cells$Obj.ID <- as.character(BivData_from_15biv_cells$Obj.ID)

#make sure 
missing_from_cell_table <- BivData_from_15biv_cells[ ! BivData_from_15biv_cells$fileName %in% Biv_Data_mean_table$fileName, ]#there are 75, objs 3 cells
#these are bivalents which don't appear the in cell level table, which can break the loop
BivData_from_15biv_cells <- BivData_from_15biv_cells[ ! BivData_from_15biv_cells$fileName %in% missing_from_cell_table$fileName, ]
#final cleaned BivData table, 2428

#loop for greping the mouse from file name ect
for(  i in 1:length( unique(BivData_from_15biv_cells$Obj.ID) ) ){

@@

  the.Q4 <- Biv_Data_mean_table$Qar.4[which( grepl(new.egg, Biv_Data_mean_table$fileName ) )]
  #the above can produe mulitple Q4

  BivData_from_15biv_cells$cell.Q4[i] <- the.Q4
  #these are just using the last index,

  the.FN <- Biv_Data_mean_table$fileName[which(grepl(new.egg, Biv_Data_mean_table$fileName ) )]

  BivData_from_15biv_cells$Q4.FN[i] <- the.FN
   # print(c(i, the.FN, the.Q4))

}

BivData_from_15biv_cells$long.Biv <- ifelse( (BivData_from_15biv_cells$chromosomeLength >= BivData_from_15biv_cells$cell.Q4), "yes", "no" )

real.long.bivData <- BivData_from_15biv_cells[BivData_from_15biv_cells$long.Biv == "yes",]

@@

#real.long.bivData
#calq the mouse averages for

Long_biv_mouse.avs_4MM <- ddply(real.long.bivData, c("mouse"), summarise,
                        Nmice = length(unique(mouse)),
                        Ncells  = length(Obj.ID),
                        mean_SC = as.numeric(format(round(  mean(chromosomeLength), 3 ), nsmall=3) ),
                        cV = cv(chromosomeLength),
                        var = as.numeric(format(round(   var(chromosomeLength),3), nsmall=3) ),
                        sd   = round(sd(chromosomeLength), 3),
                        se   = round(sd / sqrt(Ncells), 3),
                       #IFD things
                #  mean_IFD_ABS = as.numeric(format(round(  mean(IFD1_ABS, na.rm = TRUE), 3 ), nsmall=3) ),
                # mean_IFD_PER = as.numeric(format(round(  mean(IFD1_PER, na.rm = TRUE), 3 ), nsmall=3) ),

@@

Long_biv_mouse.avs_4MM <- add_sex(Long_biv_mouse.avs_4MM)
Long_biv_mouse.avs_4MM <- add_strain(Long_biv_mouse.avs_4MM)
Long_biv_mouse.avs_4MM <- add_subsp(Long_biv_mouse.avs_4MM)

Long_biv_mouse.avs_4MM$strain <- unclass(Long_biv_mouse.avs_4MM$strain)
Long_biv_mouse.avs_4MM$strain <- as.factor(Long_biv_mouse.avs_4MM$strain)

Long_biv_mouse.avs_4MM$sex <- unclass(Long_biv_mouse.avs_4MM$sex)
Long_biv_mouse.avs_4MM$sex <- as.factor(Long_biv_mouse.avs_4MM$sex)

Long_biv_mouse.avs_4MM$subsp <- unclass(Long_biv_mouse.avs_4MM$v)
Long_biv_mouse.avs_4MM$subsp <- as.factor(Long_biv_mouse.avs_4MM$subsp)

# Mouse level table

Mouse level tables are the main meat of the models. There will be several --- which account for different combinations of quality scores.

BC their for MM, format the tables for run the mixed models (unordered factors, ect)

the mouse table will be the pooled stats / summary of all SC.passing +

```{r mouse.table, echo=FALSE}

@@

#vari
Mouse.Table_BivData_4MM <- add_sex(Mouse.Table_BivData_4MM)
Mouse.Table_BivData_4MM <- add_strain(Mouse.Table_BivData_4MM)
Mouse.Table_BivData_4MM <- add_subsp(Mouse.Table_BivData_4MM)
Mouse.Table_BivData_4MM <- add_category(Mouse.Table_BivData_4MM)

@@

#remove females
Male.poly.Mouse.Table_BivData_4MM$sex <- droplevels(Male.poly.Mouse.Table_BivData_4MM$sex)
#MOLF

@@

make the melt DF for the abs (raw) foci positions and then calculated the normalized (PER) foci positions from that table

@@

MELT_Curated_BivData <- MELT_Curated_BivData[(!is.na(MELT_Curated_BivData$Pos)),]

```{r general.foci.pos, echo=FALSE, eval=FALSE}

#make the normalized foci density plots
#MELT_Curated_BivData.PER <- MELT_Curated_BivData.PER[MELT_Curated_BivData.PER$hand.foci.count < 5, ]
#MELT_Curated_BivData.PER <- MELT_Curated_BivData.PER[!MELT_Curated_BivData.PER$hand.foci.count == 0, ]

#MELT_Curated_BivData.PER <- MELT_Curated_BivData.PER[MELT_Curated_BivData.PER$PER_Position < 1.1, ]#

#remove 0 and NA
#remove 4foci count?

#check for values over 1

#density <- ggplot(MELT_Curated_BivData.PER, aes(x=PER_Position, fill=sex) ) + geom_density(alpha=.4) + facet_wrap(~hand.foci.count)+ggtitle("Normalized Foci Positions")

#density
#table(the4$mouse)
#something wrong with the 4 bivalents
#many of the lines just have 3 lines

This is proof that the plot codes work, but move the figures in the analysis doc. remeber this is just data-setup.

think about weighing the density plots by the number of bivalents per category...

@@

Main files from this script:

  1. new.Curate.FULL: cleaned up version of the passing, curated Bivalent measures

  2. OG.Curate_FULL: original version of the Bivalent data (before 'failed' SC wiped away)

  3. MELT_ABS: make melt version of foci positions for abs measuers

  4. CELL and mouse table

  5.

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.28.20.RData")
#save.image("data/BivData_4_PCA.RData")

@@

<!--
trash / junk
#Apply the cleaning steps below to the FULL-OG DF

@@

```{r telo.cent_dist, echo=FALSE}

@@

#cent_end_dist
#cent_dist

>>>>

@@

#BIVDATA MASTER SHEET
new.Curate.FULL <- read.csv("~./MLH1repo/data/BivData/curation/FULL_Curated_BivData.csv")
#83975
#83976
#83009
#80898
#80919
#61084
#60241
#60830

#Clean away all the empty rows
new.Curate.FULL <- new.Curate.FULL[!(is.na(new.Curate.FULL$fileName) | new.Curate.FULL$fileName==""), ]
#this takes a while to run

@@

```{r split.up.DF, echo=FALSE}
#new.Curate.FULL to Curated_BivData

#SC PASS
new.Curate.FULL <- new.Curate.FULL[new.Curate.FULL$SC.pass == '1',]#
#10480 #9819, #9769

@@

#don't think I need this one
#Foci_TRUE_Curate_BivData <-   Curated_BivData[(!is.na(Curated_BivData$hand.foci.count)),]
```

```{r set.type_Curated_BivData, echo=FALSE}
##change factor cols to numbers (factor -> chr -> number)
Curated_BivData$centromere_ABS_Position <- as.character(Curated_BivData$centromere_ABS_Position)
Curated_BivData$centromere_PER_Position <- as.character(Curated_BivData$centromere_PER_Position)
Curated_BivData$chromosomeLength <- as.character(Curated_BivData$chromosomeLength)

#IFD functions
#  - IFD: currently I think just does 2CO bivalents 
#  - IFD.2: for mulitple IFDs (3CO ect.)

@@

#no posittion
#just.SC.length <- Curated_BivData[is.na(Curated_BivData$Foci1),] #NAs not registering
just.SC.length <- Curated_BivData[(Curated_BivData$Foci1 == ""),]

#table(just.SC.length$category)

#decide what to do with these lines
#how will they be represented in Mat Methods?
```

@@

#10jan18_13jan17_LEW_f1_sp1_14_rev_12  '?'

##calq the nromalized.siscoten, double check the negative values;  #13sep18_28jun18_MOLF_m1_sp1_18.1_rev_14, #27aug15_12jun15_WSB_m2_sp1_18_rev_18, #21nov17_16nov17_MSM_f3_sp1_3_rev_1

#foci.pass = 2  #5aug17_14jul17_MSM_f1_sp1_13_rev_3
#hand foci =0 but there is a foci position
#too high hand foci count

@@

#neg Nrm F1
#negative.IFD2 <- Curated_BivData[which(Curated_BivData$PER_Foci_1 < 0),]
#0 really?

@@

<!--
I'm considering removing the same mice from the MLH1 counts, from the BivData, but this might -- limit the comparisons -- might be too stict. IF foci are bright and clear, SC/bivalents intact -- include.

If it seems like primary reason for excluding is low cell number include bivalents

@@

- the reasons for poor quality of the exclude mice in above list, might be from 2-3 bad bivalents -- which are removed from the biv data during the curation process. 
-->

## Strain specific BivData sets

@@

## Male specific BivData set

@@

#these measure ect should be in the male - mouse 
#isolate all musc and male
Curated_BivData_male <- Curated_BivData[ (Curated_BivData$sex == "male") & (Curated_BivData$species == "M.musculus"),]

#make strain average table
SC.Length.male_table <- ddply(Curated_BivData_male, c("strain"), summarise,
                             mean_SC = mean(chromosomeLength),
                              n_SC = length(Obj.ID),

@@

)
```

# Manual Whole Cell BivData

@@

#PER Foci
```

```{r clean.whole.cell_table, echo = FALSE, eval=FALSE}

#calq the mouse means
manual_summary_stats <- ddply(whole.cell.data_manual, c("fileName"), summarise,

                        mean_SC = as.numeric(format(round(  mean(SC.length, na.rm = TRUE), 3 ), nsmall=3) ),
                        median_SC = median(SC.length, na.rm = TRUE),
                        Qar.4 = quantile(SC.length, na.rm = TRUE)[[4]]
#                        var_SC = format(round(   as.numeric(var(SC.length)),3), nsmall=3)

manual_summary_stats <- add_mouse(manual_summary_stats)
manual_summary_stats <- add_strain(manual_summary_stats)
manual_summary_stats <- add_sex(manual_summary_stats)
manual_summary_stats <- add_subsp(manual_summary_stats)

@@

# Cell Level Table

@@

                #this below might not be correct
                     mean.IFD_2C0 = mean(   IFD1_ABS[which(hand.foci.count == 2)], na.rm = TRUE),

                       var.IFD_2CO = var( IFD1_ABS[which(hand.foci.count == 2)], na.rm=TRUE),
                       #sd.IFD_2CO   = round(sd(IFD1, na.rm=TRUE), 3),
                       #se.IFD_2CO   = round(sd.IFD / sqrt(nbivs), 3)

#cent_dis
                      mean_cent_dist = mean(dis.cent, na.rm=TRUE),
                       Qar.4 = quantile(chromosomeLength, na.rm = TRUE)[[4]] #calq threshold for all cells, pull out 'almost.whole.cells' later

#add the centromere and ifd here?
                       #mean.dist_cent = mean(dis.cent, na.rm=TRUE),
#                       var.dist_cent = var(dis.cent, na.rm=TRUE),
#                       sd.dist_cent   = round(sd(dis.cent, na.rm=TRUE), 3),
#                       se.dist_cent   = round(sd.dist_cent / sqrt(nbivs), 3),

@@

#as.data.frame( head(cell.level.BivData_table) )

@@

# Long BivData Set

@@

#1. Isolate bivalent measrues from 'almost whole cells'   (how many biv's are from cells with >15 bivalents)
over_15_biv_cell_DF <- cell.level.BivData_table[cell.level.BivData_table$Nbiv >15, ]
BivData_from_15biv_cells <- Curated_BivData[ Curated_BivData$fileName %in% over_15_biv_cell_DF$fileName, ]

@@

#check for dup
#length(duplicated(BivData_from_15biv_cells$Obj.ID))#2605
#anyDuplicated(BivData_from_15biv_cells$Obj.ID)#1997
dups.dummy <- BivData_from_15biv_cells[duplicated(BivData_from_15biv_cells$Obj.ID),]
#Dups -- 50, all from 1mar15_PWD_m1

@@

#make sure obj.id and fileName are charcter for studd below
BivData_from_15biv_cells$fileName <- as.character(BivData_from_15biv_cells$fileName)
BivData_from_15biv_cells$Obj.ID <- as.character(BivData_from_15biv_cells$Obj.ID)

#what are the Biv_Data_mean_table ... ? old version of cell table..
#replacing Biv_Data_mea_table with... cell.level.BivData_table

missing_from_cell_table <- BivData_from_15biv_cells[!BivData_from_15biv_cells$fileName %in% cell.level.BivData_table$fileName, ]#0, 
#all these files stem from

#these are bivalents which don't appear the in cell level table, which can break the loop
BivData_from_15biv_cells <- BivData_from_15biv_cells[ ! BivData_from_15biv_cells$fileName %in% missing_from_cell_table$fileName, ]
#final cleaned BivData table, 2428

#2. calq the Q4 threshold
#loop for greping the mouse from file name ect

#mini.now  <- BivData_from_15biv_cells[1:300,]
#broken again -- confusion between the number Q4 and the fileName

for(  i in 1:length( unique(BivData_from_15biv_cells$Obj.ID) ) ){

  #print(c(i, " the i") )

@@

  the.Q4 <- cell.level.BivData_table$Qar.4[ which( grepl(new.egg, cell.level.BivData_table$fileName ) )]
  #there is no Qar4 in this DF

  #print(c("the Q4  ",the.Q4)  )

  #the above can produe mulitple Q4

  BivData_from_15biv_cells$cell.Q4[i] <- the.Q4
  #these are just using the last index,
  #this might be wrong....

  the.FN <- as.character(cell.level.BivData_table$fileName[which(grepl(new.egg, cell.level.BivData_table$fileName ) )] )

  BivData_from_15biv_cells$Q4.FN[i] <- as.character(the.FN)  #this FN is NOT RIGHT
   # print(c(i, the.FN, the.Q4))
}

#3.mark which bivalents are above the threshold
#WHY DOESN"T THIS WORK?

BivData_from_15biv_cells$long.Biv <- ifelse( (BivData_from_15biv_cells$chromosomeLength >= as.numeric(BivData_from_15biv_cells$cell.Q4)  ), "yes", "no" )

real.long.bivData <- BivData_from_15biv_cells[BivData_from_15biv_cells$long.Biv == "yes",]#713 observations
```

The above blocks of code 1) isolates bivalents measures from cells with >15 segmented bivalents 2) for the cells in these data calculates the Q4 threshold and 3) marks which bivalents are longer than the threshold.

@@

# make a table for the Mixed Models -- from the long.BivData
# Calq mouse averages

#add in all the other stats there are in the other tables

Long.biv_mouse_table <- ddply(real.long.bivData, c("mouse"), summarise,

                              Nmice = length(unique(mouse)),
                        Ncells  = length(Obj.ID),

                          mean_SC = as.numeric(format(round(  mean(chromosomeLength), 3 ), nsmall=3) ),

                        cV = cv(chromosomeLength),
                        var = as.numeric(format(round(   var(chromosomeLength),3), nsmall=3) ),
                        sd   = round(sd(chromosomeLength), 3),
                        se   = round(sd / sqrt(Ncells), 3),

                        #SC lengths by class
                        nCO0 =  sum(hand.foci.count == 0, na.rm=TRUE), 
                      nCO1 =  sum(hand.foci.count == 1, na.rm=TRUE), 
                       nCO2 = sum(hand.foci.count == 2, na.rm=TRUE),
                       nCO3 = sum(hand.foci.count == 3, na.rm=TRUE),
                       nCO4 = sum(hand.foci.count == 4, na.rm=TRUE),

                      mean.siscoten_0CO = mean(SisCoTen[which(hand.foci.count == 0)], na.rm = TRUE),
                      mean.siscoten_1CO = mean(SisCoTen[which(hand.foci.count == 1)], na.rm = TRUE),
                     mean.siscoten_2CO = mean(SisCoTen[which(hand.foci.count == 2)], na.rm = TRUE),
                      mean.siscoten_3CO = mean(SisCoTen[which(hand.foci.count == 3)], na.rm = TRUE),

                #  mean_IFD_ABS = as.numeric(format(round(  mean(IFD1_ABS, na.rm = TRUE), 3 ), nsmall=3) ),
                # mean_IFD_PER = as.numeric(format(round(  mean(IFD1_PER, na.rm = TRUE), 3 ), nsmall=3) ),

@@

        #          mean_siscoten = mean(siscoten)
        #
)
#mouse averages for long.biv

Long.biv_mouse_table <- add_sex(Long.biv_mouse_table)
Long.biv_mouse_table <- add_strain(Long.biv_mouse_table)
Long.biv_mouse_table <- add_subsp(Long.biv_mouse_table)
Long.biv_mouse_table <- add_category(Long.biv_mouse_table)

#unordered for the mixed models (move this to the MM blocks...?)
Long.biv_mouse_table$subsp <- factor(Long.biv_mouse_table$subsp, ordered = FALSE)
Long.biv_mouse_table$sex <- factor(Long.biv_mouse_table$sex, ordered = FALSE)
Long.biv_mouse_table$strain <- factor(Long.biv_mouse_table$strain, ordered = FALSE)

#long.biv. 1) HetC  2) male.poly (the main factors are still unordered)

#1) Long Biv for 
#remove all the non-used strains!!
Long.biv_mouse_table_HetC <- Long.biv_mouse_table

Long.biv_mouse_table_HetC <- Long.biv_mouse_table_HetC[Long.biv_mouse_table$strain != "AST",]
Long.biv_mouse_table_HetC <- Long.biv_mouse_table_HetC[Curated_BivData$strain != "TOM",]
Long.biv_mouse_table_HetC <- Long.biv_mouse_table_HetC[Long.biv_mouse_table_HetC$strain != "CZECH",]
Long.biv_mouse_table_HetC$strain <- droplevels(Long.biv_mouse_table_HetC$strain)

#table(droplevels( Long.biv_mouse_table_HetC$category) )  #for double checking

#2) Long Biv for male.poly
#just males, just Musculus
Long.biv_mouse_table_male.poly <- Long.biv_mouse_table

Long.biv_mouse_table_male.poly <- Long.biv_mouse_table_male.poly[Long.biv_mouse_table_male.poly$sex == "male",]

#table(droplevels( Long.biv_mouse_table_male.poly$category) ) #for double checking
```

The above code chunk makes 2 mouse level tables; **Long.biv_mouse_table_HetC** and **Long.biv_mouse_table_male.poly**. Run these through the model systems.

# Mouse Level Tables

Mouse level tables are the main meat of the models. There will be several for use in different models. Format these tables for run the mixed models (unordered factors, ect).

```{r FULL.mouse.table, echo=FALSE}

@@

#
Mouse.Table_BivData_4MM <- add_sex(Mouse.Table_BivData_4MM)
Mouse.Table_BivData_4MM <- add_strain(Mouse.Table_BivData_4MM)
Mouse.Table_BivData_4MM <- add_subsp(Mouse.Table_BivData_4MM)
Mouse.Table_BivData_4MM <- add_category(Mouse.Table_BivData_4MM)

@@

#remove females
Male.poly.Mouse.Table_BivData_4MM$sex <- droplevels(Male.poly.Mouse.Table_BivData_4MM$sex)

@@

The BivData MELT DF is primarily for the nrmF1.pos plots/analysis. It is a Melted DF for raw and normalized foci positions from the Curated_BivData.

@@

MELT_Curated_BivData <- MELT_Curated_BivData[(!is.na(MELT_Curated_BivData$Pos)),]
```

@@

  7. mouse table (full/all mice)

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_3.2.20.RData")
#save.image("data/BivData_4_PCA.RData")

@@

<!--
trash / junk

#Apply the cleaning steps below to the FULL-OG DF

@@

```{r telo.cent_dist, echo=FALSE, eval=FALSE}

@@

#cent_end_dist
#cent_dist
```
